Paper 1

### 2022-05-29 scripts/Paper 1.Rmd
add jday to rainfall

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-1]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[3] <- "jday"
colnames(rainfall_L)[2] <- "month"
rainfall_L$Site <- "L"

@@

@@

TSData <- rainfall[, 1] # ts data
decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
plot (decomposedRes) # see plot below
stlRes <- stl(tsData, s.window = "periodic")
```

>>>>

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-1]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[3] <- "day"
colnames(rainfall_L)[2] <- "month"
rainfall_L$Site <- "L"
rainfall_L$date <- as.Date(with(rainfall_L, paste(Year, month, day,sep="-")), "%Y-%m-%d")
rainfall_L$jday <- yday(rainfall_L$date)

@@

```{r create new dataframe for timeseries analysis}
rainfall.2merge <- rainfall %>% filter(Year == 2019  & jday < 354)
input.daily$Site <- "SP"

tsData <- rbind.fill(rainfall.2merge, input.daily) %>% 
  select(Year, month, jday, Precip, NEE_LT.gC, ER_LT.gC, GPP_LT.gC) %>%
  mutate(
    NEE2weeks = lag(NEE_LT.gC, n = 14, default = NA)
  )

tsData$date <- as.Date(with(tsData, paste(Year, month, jday,sep="-")), "%Y-%m-%d")
lm1 <- lm(NEE2weeks~Precip, tsData)
summary(lm1)

lm2 <- lm(NEE_LT.gC~Precip, tsData)
summary(lm2)
```

@@
